Parsing Tweets into Universal Dependencies

### 2018-04-16 paper.tex
SVA
Noah

\section{Introduction}
NLP for social media messages is challenging, because domain
adaptation is required, and also because creating annotated datasets
(e.g., treebanks)
for training.
Pioneering work by \citet{Foster:2011:HPT:2908630.2908634} 
annotated 7,630 tokens' worth of tweets according to the
phrase-structure conventions of the Penn Treebank
\citep[PTB;][]{Marcus93buildinga}, enabling conversion to Stanford Dependencies.
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank}),
consisting of 12,149 tokens and largely following conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
\citet{Yamada03statisticaldependency} dependencies (without labels). 
Both annotation efforts were highly influenced by the PTB, whose guidelines
have good grammatical coverage on newswire. However, when it comes
to informal, unedited, user-generated text, the guidelines may leave
many annotation decisions unspecified.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

%In the syntax annotation, tweet specific
%constructions are considered by both \citet{sanguinetti-17} and our paper.
With respect to tweet-specific constructions,
\citeposs{sanguinetti-17} and our  interpretation of headedness are the same, 
but we differ in the relation label.
For topical hashtags, we use \textit{discourse} while they used \textit{parataxis}. 
In referential URLs, we use \textit{list} (following the precedent of UD\_English-EWT) while they used \textit{dep}.
%<<<<<<< HEAD
%The choice of relation on the non-syntactic tokens is questionable
%since UD doesn't specify a convention for this. 
%Our choice of \textit{discourse} is inspired by the observation that emoticon is annotated as \textit{discourse}.
%\citet{sanguinetti-17} used the same relation for the emoticon but analyze topical hashtag as \textit{parataxis}.%\nss{what did PosTWITA-UD use for non-syntactic tokens?}\yjcomment{done}
%=======
%The choice of relation on the non-syntactic tokens is questionable
%since UD doesn't specify a convention for this. 
Our choice of \textit{discourse} for sentiment emoticons
is inspired by the observation that emoticons are annotated as \textit{discourse} by UD\_English-EWT;
\citet{sanguinetti-17} used the same relation for the emoticons.
Retweet constructions and truncated words were not explicitly touched
by \citet{sanguinetti-17}.
Judging from the released treebank\footnote{\url{https://github.com/UniversalDependencies/UD_Italian-PoSTWITA}}, the \textit{RT} marker, at-mention, and colon in the retweet construction are all attached to the predicate of the following sentence with \textit{dep}, \textit{vocative:mention} and \textit{punct}.
%\nss{how does the other treebank treat the RT construction and truncated words?}
%\nss{topical hashtags already mentioned above}
%>>>>>>> a7f86b777a73f64b2f05101f4804421aea0412f3
% Non-syntactic tokens can be easily recovered
% from our annotation and changing it to other relation in the future development is not difficult.
We expect that the official UD guidelines will eventually adopt standards for these constructions so the treebanks can be harmonized.

>>>>

\section{Introduction}
NLP for social media messages is challenging, requiring domain
adaptation and annotated datasets
(e.g., treebanks)
for training and evaluation.
Pioneering work by \citet{Foster:2011:HPT:2908630.2908634} 
annotated 7,630 tokens' worth of tweets according to the
phrase-structure conventions of the Penn Treebank
\citep[PTB;][]{Marcus93buildinga}, enabling conversion to Stanford Dependencies.
\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
annotating tweets and presented a tweet treebank ({\sc Tweebank}),
consisting of 12,149 tokens and largely following conventions
suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
\citet{Yamada03statisticaldependency} dependencies (without labels). 
Both annotation efforts were highly influenced by the PTB, whose guidelines
have good grammatical coverage on newswire. However, when it comes
to informal, unedited, user-generated text, the guidelines may leave
many annotation decisions unspecified.
%Motivation notes:  explain why UD is attractive (and more attractive
%than what previous work used, which was based on YM).  one reason is
%that it might allow sharing of texts annotated in different genres (or
%even languages, cite Waleed).  but universal annotation schemes are
%challenging!  this paper contends with the challenges of
%applying UD to social media texts.

@@

%In the syntax annotation, tweet specific
%constructions are considered by both \citet{sanguinetti-17} and our paper.
With respect to tweet-specific constructions,
\citeposs{sanguinetti-17} and our  interpretations of headedness are the same, 
but we differ in the relation label.
For topical hashtags, we use \textit{discourse} while they used \textit{parataxis}. 
In referential URLs, we use \textit{list} (following the precedent of UD\_English-EWT) while they used \textit{dep}.
%<<<<<<< HEAD
%The choice of relation on the non-syntactic tokens is questionable
%since UD doesn't specify a convention for this. 
%Our choice of \textit{discourse} is inspired by the observation that emoticon is annotated as \textit{discourse}.
%\citet{sanguinetti-17} used the same relation for the emoticon but analyze topical hashtag as \textit{parataxis}.%\nss{what did PosTWITA-UD use for non-syntactic tokens?}\yjcomment{done}
%=======
%The choice of relation on the non-syntactic tokens is questionable
%since UD doesn't specify a convention for this. 
Our choice of \textit{discourse} for sentiment emoticons
is inspired by the observation that emoticons are annotated as \textit{discourse} by UD\_English-EWT;
\citet{sanguinetti-17} used the same relation for the emoticons.
Retweet constructions and truncated words were not explicitly touched
by \citet{sanguinetti-17}.
Judging from the released treebank\footnote{\url{https://github.com/UniversalDependencies/UD_Italian-PoSTWITA}}, the \textit{RT} marker, at-mention, and colon in the retweet construction are all attached to the predicate of the following sentence with \textit{dep}, \textit{vocative:mention} and \textit{punct}.
%\nss{how does the other treebank treat the RT construction and truncated words?}
%\nss{topical hashtags already mentioned above}
%>>>>>>> a7f86b777a73f64b2f05101f4804421aea0412f3
% Non-syntactic tokens can be easily recovered
% from our annotation and changing it to other relation in the future development is not difficult.
We expect that the official UD guidelines will eventually adopt standards for these constructions so the treebanks can be harmonized.
